Proportional multi-state multiple-cohort life table model

### 2018-05-08 MSLT/MSLTdoc.Rmd
tried a loop of aggregated outcomes, did not work

```{r echo=FALSE, out.width='100%'}
## Loop to include graphs in the document
graphs_doc <- list()
index <- 1
for (age in i_age_cohort) {
      for (sex in i_sex)  {
        for (outcome in i_outcome) {

graphs_doc [[index]] <- c(paste("graphs/",age,"_",sex,"_", outcome,".tiff", sep = ""))
          knitr::include_graphics(graphs_doc [[index]]) 
          # %>%
          #   set_names(paste("Change in", ifelse(outcome == "mx", "Deaths", "Incidence"), "over time", sep = ""))

          index <- index + 1
        }
    }
}
```

```{r, echo=FALSE}
## fig.cap=paste(names(graphs_doc)), message=FALSE, 
 knitr::include_graphics(graphs_doc[c(1:64)])
```

24) Add up all outcomes per year of simulation with generated function.

@@

aggregate_frame_males <- gen_aggregate(in_data = output_df, in_cohorts = 16, in_population = "male", in_outcomes = c('Lx_bl','Lx_sc', "Lx_diff"))

aggregate_frame_females <- gen_aggregate(in_data = output_df, in_cohorts = 16, in_population = "female", in_outcomes = c('Lx_bl','Lx_sc', "Lx_diff"))

@@

## Create a copy of aggregate_frame_females
total_aggr <- aggregate_frame_females
## Add aggregate_frame_males values to it
for (i in 1:ncol(aggregate_frame_females)){
  total_aggr[i] <- total_aggr[i] + aggregate_frame_males[i]
}
total_aggr$sim_year <- seq.int(nrow(total_aggr))

## Uncomment to view aggregated data
sum(total_aggr$total_Lx_diff)
```

@@

disease_outcome <- "Life years"

@@

  geom_line(mapping = aes(y = total_Lx_bl, colour = "total_Lx_bl")) +
  theme_classic() +
  geom_hline(yintercept=0, linetype="dashed", color = "black") +
  geom_line(mapping = aes(y = total_Lx_sc, colour = "total_total_Lx_sc")) +
  geom_line(mapping = aes(y = total_Lx_diff, colour = "total_Lx_diff")) +
  xlab ("Simulation years") + ylab ("Cases") + labs (title = paste(disease_outcome)) +
  theme(plot.title = element_text(hjust = 0.5, size = 12)) +
  scale_color_discrete(name = paste(""), labels = c("Baseline", "Difference", "Scenario")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_y_continuous(breaks=seq(0,7000000,by=1000000))

#Print to view
print(total_plot)
```
#Comments

>>>>

```{r echo=FALSE, out.width='100%'}
## Loop to include graphs in the document

## MAY NOT NEED THIS ONE
graphs_doc <- list()
index <- 1
for (age in i_age_cohort) {
      for (sex in i_sex)  {
        for (outcome in i_outcome) {

graphs_doc [[index]] <- c(paste(output_dir, "/",age,"_",sex,"_", outcome,".jpeg", sep = ""))
knitr::include_graphics(graphs_doc [[index]])

          index <- index + 1
        }

 knitr::include_graphics(graphs_doc[c(1:64)])
```

24) Add up all outcomes per year of simulation with generated function. BETTER TO HAVE A LOOP, I TRIED BY LOOPING IN THE FUNCITON ARGUMENT I_OUTCOMES, BUT THIS DID NOT WORK. THEN, IF LOOP HERE ALSO IN NEXT CODE.

@@

aggregate_frame_males <- gen_aggregate(in_data = output_df, in_cohorts = 16, in_population = "male", in_outcomes = c('inc_num_bl_ihd','inc_num_sc_ihd', "inc_num_diff_ihd"))

aggregate_frame_females <- gen_aggregate(in_data = output_df, in_cohorts = 16, in_population = "female", in_outcomes = c('inc_num_bl_ihd','inc_num_sc_ihd', "inc_num_diff_ihd"))

@@

## Create a copy of aggregate_frame_females
total_aggr <- aggregate_frame_females
## Add aggregate_frame_males values to it
for (i in 1:ncol(aggregate_frame_females)){
  total_aggr[i] <- total_aggr[i] + aggregate_frame_males[i]
}
total_aggr$sim_year <- seq.int(nrow(total_aggr))
```

@@

disease_outcome <- "Incidence of Ischemic Heart Disease"

@@

  geom_line(mapping = aes(y = total_inc_num_bl_ihd, colour = "total_inc_num_bl_ihd")) +
  theme_classic() +
  geom_hline(yintercept=0, linetype="dashed", color = "black") +
  geom_line(mapping = aes(y = total_inc_num_sc_ihd, colour = "total_inc_num_sc_ihd")) +
  geom_line(mapping = aes(y = total_inc_num_diff_ihd, colour = "total_inc_num_diff_ihd")) +
  xlab ("Simulation years") + ylab ("Cases") + labs (title = paste(disease_outcome)) +
  theme(plot.title = element_text(hjust = 0.5, size = 12)) +
  scale_color_discrete(name = paste(""), labels = c("Baseline", "Difference", "Scenario")) +
  theme(plot.title = element_text(hjust = 0.5))

#Print to view
print(total_plot)

#Comments
